The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-19 document/ms.tex
formatting
removing comment
intro minor TDM edits

\usepackage{endnotes}
\let\footnote=\endnote

@@

\linespread{0.54} % close to 10/13 spacing in ``manuscript''
\setlength{\parindent}{0.54\baselineskip}
\hypersetup{colorlinks = false}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
With modifications by David W. Hogg and Daniel Foreman-Mackey\\
See the last page for endnotes
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\makeatother

@@

Before the launch of the \kepler\ Mission, it was predicted that the nominal
mission would discover at least 10 exoplanets with only one or two observed
transits \citep{Yee:2008} and subsequent searches for these signals have
already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
However, the systematic study of the population of long-period exoplanets
found in the \kepler\ data has, so far, been limited because of the
substantial technical challenge and the subtleties of interpretation.
Any single transit events discovered in the \kepler\ light curves are
interesting in their own right but the development of a general and systematic
method for the discovery of planets with orbital periods longer than the
survey baseline are crucial for the future of of exoplanet research with the
transit method.
All future transit surveys have shorter observational baselines than the
\kepler\ Mission (\KT, \citealt{Howell:2014}; \tess, \citealt{Ricker:2015};
\plato, \citealt{Rauer:2014}) and given suitable techniques, single transit
events will be plentiful and easily discovered.
The methodological framework presented in the following pages is a candidate
for this task and it could be modified and applied to these forthcoming data
sets as they are collecting in the upcoming years.

A study of the population of long-period transiting planets complements
parallel radial velocity \citep[for example][]{Cumming:2008,
Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.
Exoplanets with both mass and radius measurements can be used to study
planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
The existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods and discoveries with the transit method are
compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to planets at the detection limits of the current state-of-the-art
radial velocity surveys.

@@

In this \paper, we develop a systematic method for reliably discovering the
transits of large long-period companions in photometric time series
\emph{without human intervention}.
Since the search methodology is fully automated, we can robustly measure the
search completeness~--~using injection and recovery tests~--~and use these
products to place probabilistic constraints on the occurrence rate of
long-period planets.
We apply this method to a subset of the archival data from the \kepler\
Mission, release a catalog of exoplanet candidates, and estimate the
occurrence rate of long-period exoplanets.
We finish by discussing the potential effects of false positives, the
prospects for follow-up, and compare to calculated occurrence rate to results
based on discoveries using different planet discovery methods.

@@

\subsection{Target selection}\sectlabel{target-selection}

@@

% This occurrence rate estimate~--~and all other results based on transit
% surveys~--~is affected by Malmquist bias.
% For a transit survey, this bias enters in two ways: \emph{(a)} contamination
% of the sample by giants, and \emph{(b)} discrepancy

@@

\dfmtodo{More words here about comparison.}

@@

\theendnotes

>>>>

% \usepackage{endnotes}
% \let\footnote=\endnote

@@

\linespread{0.54} % close to 10/13 spacing in ``manuscript''
\setlength{\parindent}{0.54\baselineskip}
\hypersetup{colorlinks = false}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
With modifications by David W. Hogg and Daniel Foreman-Mackey
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\makeatother

@@

Before the launch of the \kepler\ Mission, it was predicted that the nominal
mission would discover at least 10 exoplanets with only one or two observed
transits \citep{Yee:2008} and subsequent searches for these signals have
already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
However, the systematic study of the population of long-period exoplanets
found in the \kepler\ data has, so far, been limited because of the
substantial technical challenge and the subtleties of interpretation.
Any single transit events discovered in the \kepler\ light curves are
interesting in their own right but the development of a general and systematic
method for the discovery of planets with orbital periods longer than the
survey baseline is crucial for the future of of exoplanet research with the
transit method.
All future transit surveys have shorter observational baselines than the
\kepler\ Mission (\KT, \citealt{Howell:2014}; \tess, \citealt{Ricker:2015};
\plato, \citealt{Rauer:2014}) and given suitable techniques, single transit
events will be plentiful and easily discovered.
The methodological framework presented in the following pages is a candidate
for this task.% and it could be modified and applied to these forthcoming data
%sets as they are collecting in the upcoming years.

A study of the population of long-period transiting planets complements
parallel radial velocity \citep[for example][]{Cumming:2008,
Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016} \dfmtodo{incomplete sentence?}.
Exoplanets with both mass and radius measurements can be used to study
planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
The existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods and discoveries with the transit method are
compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to planets at the detection limits of the current state-of-the-art
radial velocity surveys.

@@

In this \paper, we develop a systematic method for reliably discovering the
transits of large long-period companions in photometric time series
\emph{without human intervention}.
Since the search methodology is fully automated, we can robustly measure the
search completeness~--~using injection and recovery tests~--~and use these
products to place probabilistic constraints on the occurrence rate of
long-period planets.
We apply this method to a subset of the archival data from the \kepler\
Mission, present a catalog of exoplanet candidates, and estimate the
occurrence rate of long-period exoplanets.
We finish by discussing the potential effects of false positives, evaluating the
prospects for follow-up, and comparing our results to other studies
based on different planet discovery methods.

@@

\newpage
\subsection{Target selection}\sectlabel{target-selection}

@@

@@

\dfmtodo{More words here about comparison and interpretation.}

@@

% \theendnotes
